Panel Seminars

### 2023-10-05 index.Rmd
changed index and yaml per previous commit

* [Multifactorial RNAseq analyses](FUN_01_DGE_comparison_v2.html)  
* Align and count RNAseq reads (coming soon!)
    * De novo, reference-based, and Tag-seq methods

>>>>

* [Multifactorial RNAseq analyses](DGE_comparison_v2.html)  
* Align and count RNAseq reads (coming soon!)
    * De novo, reference-based, and Tag-seq methods
